\Title

### 2023-02-10 Grimaldi-etal-BiolCybernetics.tex
Methods : 2.4

\subsection{Supervised learning of the motion detection task}
Since the model is fully differentiable, we can now implement a semi-supervised learning rule. The loss function of the MLR model is the binary cross-entropy on the output of the classification layer. Supervision was implemented using the input binary events as defined above and the motion direction labels as the desired output. The labels were defined at each time point as a one-hot encoding of the current motion in the channel corresponding to the current motion for all positions. As in this semi-supervised context, the label is known, but the timing is not, we used a selection of the temporal support in an unsupervised manner. It is important to note that we weighted the cost function by considering only active cells, such that the error is only back propagated to the spatial locations of these most active cells. This is reminiscent of previous methods solving this problem using a Winner-Takes-All mechanism~\citep{masquelier_unsupervised_2007}. Simulations are performed with the \note{PyTorch library using gradient descent with Adam (for $2^{12}$ movies and a learning rate of $10^{-5}$)}. We demonstrated in a previous work that this type of learning algorithm can be assimilated to a Hebbian learning mechanism~\cite{grimaldi_robust_2022}.  

>>>>

\subsection{Supervised learning of the motion detection task}
%
Since the model is fully differentiable, we can now implement a semi-supervised learning rule. The loss function of the MLR model is the binary cross entropy on the output of the classification layer. Supervision was implemented using the binary input events as defined above and the motion direction labels as the desired output. The labels were defined at each time point as a one-hot encoding of the current motion in the channel corresponding to the current motion for all positions. Since in this semi-supervised context the label is known but the timing is not, we used a selection of the temporal support in an unsupervised manner. It is important to note that we weighted the cost function by considering only active cells, so that the error is only propagated back to the spatial locations of these most active cells. This is reminiscent of previous methods that solve this problem using a winner-takes-all mechanism~\citep{masquelier_unsupervised_2007}. Simulations are performed with the \note{PyTorch library using gradient descent with Adam (for $2^{12}$ movies and a learning rate of $10^{-5}$)}. We have shown in a previous work on a simplified task using synthetic textures that this type of learning algorithm can be assimilated to a Hebbian learning mechanism~\cite{grimaldi_robust_2022}.
